He-Man: A domain-specific language for lightweight concurrency

### 2012-03-06 paper/paper.tex
Add important citation.

We present He-Man, a compiled, embedded, domain specific language in Haskell for
building scalable network applications in a natural, straight-line manner while
still producing efficient event loop-based code. He-Man programs are compact and
measurements indicate that it performs acceptably. Our implementation is
available at
\url{https://github.com/msullivan/he-man}.
\end{abstract}

@@

\begin{figure}[ht]
\centering
\bnf{
\i{Thread}
\p{(\i{thread\_label}, [(\i{Var}, \i{Type})])}
\i{Block}
\p{(\i{label}, \i{thread\_label}, [\i{Stmt}], \i{Tail})}
\i{Tail}
\p{\b{Goto} \i{label}}
\a{\b{GotoWait} \i{label}}
\a{\b{If} \i{Expr} \i{Tail} \i{Tail}}
\a{\b{Exit}}
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Spawn} \i{label} [((\i{Var}, \i{Type}), \i{Expr})]}
}
\caption{Back-end abstract syntax.}
\label{fig:back-syntax}
\end{figure}

>>>>

We present He-Man \cite{HeMan}, a compiled, embedded, domain specific language in Haskell for
building scalable network applications in a natural, straight-line manner while
still producing efficient event loop-based code. He-Man programs are compact and
measurements indicate that it performs acceptably. Our implementation is
available at
\url{https://github.com/msullivan/he-man}.
\end{abstract}

@@

\begin{figure}[ht]
\centering
\bnf{
\i{Thread}
\p{(\i{thread\_label}, [(\i{Var}, \i{Type})])}
\i{Block}
\p{(\i{label}, \i{thread\_label}, [\i{Stmt}], \i{Tail})}
\i{Tail}
\p{\b{Goto} \i{label}}
\a{\b{GotoWait} \i{Expr} \i{label}}
\a{\b{If} \i{Expr} ([\i{Stmt}], \i{Tail}) ([\i{Stmt}], \i{Tail})}
\a{\b{Exit}}
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Spawn} \i{label} [((\i{Var}, \i{Type}), \i{Expr})]}
}
\caption{Back-end abstract syntax.}
\label{fig:back-syntax}
\end{figure}
